\textbf{Linear Algebra}\\A summary for MIT 18.06SC

### 2020-06-30 skills/math/linear_algebra_summary.tex
update

\subsection{Permutation of matrices}
For any matrix $\mA$, we can swap its rows by multiplying a \textit{permutation matrix } $\mP$ on the left of $\mA$. For example,
\begin{align}
	\mP \mA = \begin{bmatrix}
		0 &0&1\\1 & 0 & 0\\ 0 & 1 & 0 
	\end{bmatrix}  \begin{bmatrix}
		a_1\\a_2\\ a_3
	\end{bmatrix}  = \begin{bmatrix}
		a_3\\a_1\\ a_2
	\end{bmatrix}
\end{align}
where $a_k$ refers to the $k$-th row of $\mA$. The inverse of permutation matrix $\mP$ is $\mP^{-1} = \mP^T$, which implies the orthogonality of permutation matrix. For an $n \times m$ matrix, there are $n!$ different row permutation matrices, which form a \textit{multiplicative group}.

\vspace{.2cm}
Similarly, we can also swap the columns of the matrix $\mA$ by multiplying a permutation matrix on the right of $\mA$.

>>>>

\subsection{Permutation of matrices}
For any matrix $\mA$, we swap its rows by multiplying a \textit{permutation matrix } $\mP$ on the left of $\mA$. For example,
\begin{align}
	\mP \mA = \begin{bmatrix}
		0 &0&1\\1 & 0 & 0\\ 0 & 1 & 0 
	\end{bmatrix}  \begin{bmatrix}
		a_1\\a_2\\ a_3
	\end{bmatrix}  = \begin{bmatrix}
		a_3\\a_1\\ a_2
	\end{bmatrix}
\end{align}
where $a_k$ refers to the $k$-th row of $\mA$. The inverse of permutation matrix $\mP$ is $\mP^{-1} = \mP^T$, which implies the orthogonality of permutation matrix. For an $n \times m$ matrix, there are $n!$ different row permutation matrices, which form a \textit{multiplicative group}.

\vspace{.2cm}
Similarly, we also swap the columns of the matrix $\mA$ by multiplying a permutation matrix on the right of $\mA$.
